---
title: "Shared Housework Tasks in Heterosexual and Same-sex Couples"
author: "Kamila Kolpashnikova"
date: '2022-09-17'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, include=FALSE}
library(dplyr)
library(stargazer)
library(gtsummary)
library(flextable)
```

Overview
--------

The code in this replication project uses data from GSS 2017 and analyzes shared domestic tasks among heterosexual and same-sex couples it using R. One master (shell) file runs all of the scripts, which are located in the 'src' folder, and creates tables, which can be found in 'output' folder. The replicator should expect the code to run for a few minutes.

Data Availability and Provenance Statements
----------------------------

The data for this project (Canadian General Social Survey 2017) may be obtained from Statistics Canada. Researchers interested in access to the data may contact Client Services and Dissemination at (613) 951-5979, by fax at (613) 951-0387 or by e-mail at sasd-dssea@statcan.gc.ca. PUMF files can be made available by Statistics Canada.

### Statement about Rights

- [X] I certify that the author(s) of the code in this repository have legitimate access to and permission to use the data used in this manuscript. 


### (Optional, but recommended) License for Data

The code is licensed under a GNU Affero General Public License. See [LICENSE.md](LICENSE.md) for details.


### Summary of Availability

- [ ] All data **are** publicly available.
- [X] Some data **cannot be made** publicly available (through Statistics Canada).
- [ ] **No data can be made** publicly available.

### Details on each Data Source

The file used in these scripts is "gss-12M0025-E-2017-c-31_F1.csv". Data dictionary and details can be downloaded from [Statistics Canada](https://www150.statcan.gc.ca/n1/pub/45-25-0001/cat4/c31_2017.zip).

Computational requirements
---------------------------

Code presented here was run on Windows OS (Windows 10 Pro).

### Software Requirements

- R 4.2.1
  - packages are listed in renv.lock
  - the renv package will install all dependencies other programs. Install renv package, load it, and run renv::restore().

### Memory and Runtime Requirements

The code is not memory intensive.

#### Summary

Approximate time needed to reproduce the analyses on a standard 2022 Windows machine:

- [X] <10 minutes
- [ ] 10-60 minutes
- [ ] 1-8 hours
- [ ] 8-24 hours
- [ ] 1-3 days
- [ ] 3-14 days
- [ ] > 14 days
- [ ] Not feasible to run on a desktop machine, as described below.

#### Details

The code was last run on a *Intel(R) Core(TM) i7-10610U CPU @ 1.80GHz 2.30 GHz**. 
RAM 32.0 GB

Description of programs/code
----------------------------

- Script in `src/RUNALL.R` will run all the scripts
- Script in `src/cleaning.R` will load the GSS data and re-code variables.
- Script in `src/analytic_sample.R` subsets the sample to keep only the variables and observations that will be needed for the subsequent analyses.
- Script in `src/descriptive_stats.R` will generate a descriptive statistics table for main variables and store it in 'output' folder. 
- Script in `src/regression_models.R` will generate regression models for the total sample and for subsamples of respondents in heterosexual and same-sex couples.

Instructions to Replicators
---------------------------

- clone the repository
- set the main 'reproducibility-project' as the working directory
- install and load renv package 

```{r eval=FALSE}
install.packages("renv")
library(renv)
```

- load packages from the renv 

```{r eval=FALSE}
renv::restore() 
```

- Create 'data' folder and download the data file into it. 
- Run the following command to run all

```{r eval=FALSE}
source("src/RUNALL.R")
```


List of tables and programs
---------------------------

The provided code reproduces:

- [ ] All numbers provided in text in the paper
- [X] All tables and figures in the paper
- [ ] Selected tables and figures in the paper, as explained and justified below.


| Figure/Table #    | Program                  | Line Number | Output file                      | Note                            |
|-------------------|--------------------------|-------------|----------------------------------|---------------------------------|
| Table 1           | src/descriptive_stats.R  |25-43        | Table_1.docx                     ||
| Table 2           | src/regression_models.R  |3-30         | Table_2.doc                      ||
      |

## References

Statistics Canada. 2020. General Social Survey, Cycle 31, 2017 [Canada]: Family (version 2020-09). Statistics Canada [producer and distributor], accessed September 10, 2021. ID: gss-12M0025-E-2017-c-31

---

## Acknowledgements

Some content on this page was copied from [Hindawi](https://www.hindawi.com/research.data/#statement.templates). Other content was adapted  from [Fort (2016)](https://doi.org/10.1093/restud/rdw057), Supplementary data, with the author's permission.
